Generating Simulated Data

### 2021-04-13 docs/SimData.Rmd
new equal binwidths and lengths

*Consider a function to do this using species max size, the vonB k and the desired number of bins for more consistency and to easily change Nsizebins.* Do we need t0 as well? Haven't saved it.

@@

  #aggregate bins in multiples of optimal for bigger fish/slower growth to get Nsizebins
  ifelse(binwidth.max > bindef, #& binwidth.max < 0.5*Lmax,
         binwidths <- c(rep(binwidth.gro, Nsizebins-1), binwidth.max),
         binwidths <- rep(bindef, Nsizebins))

@@

>>>>

*Consider a function to do this using species max size, the vonB k and the desired number of bins for more consistency and to easily change Nsizebins.*

This function is below, but with only 5 bins I don't likw how it works, allocating more smaller bins to the smallest sizes that we don't observe and aggregating many lengths into one large bin. Therefore the simplest approach is to have equal sized bins (max observed length/desired number of bins). We will try this for the length comps.

@@

  #aggregate bins in multiples of optimal for bigger fish/slower growth to get Nsizebins
  ifelse(binwidth.max > bindef & binwidth.max < 0.5*Lmax,
         binwidths <- c(rep(binwidth.gro, Nsizebins-1), binwidth.max),
         binwidths <- rep(bindef, Nsizebins))

@@

equalbinwidths <- function(Lmax, Nsizebins){
  bindef <- max(1,ceiling(Lmax/Nsizebins))
  binwidths <- rep(bindef, Nsizebins)
  return(binwidths)
}

# for fixed bins across surveys find min and max observed lengths

maxLrange <- bind_rows(minmaxvonBK) %>%
  group_by(species) %>%
  summarise(minminL = min(minlen),
            maxmaxL = max(maxlen))

Nsizebins  <-  5

newbins <- maxLrange %>%
  group_by(species) %>%
  group_modify(~broom::tidy(equalbinwidths(.$maxmaxL, Nsizebins))) %>%
  mutate(lb = paste0("sizebin",seq(1:Nsizebins))) %>%
  pivot_wider(names_from = lb, values_from = x)

sizebins <- as.data.frame(newbins) %>%
  rename('commentField-notused' = species) %>%
  relocate('commentField-notused', .after = last_col())
